Transmembrane helices are an over-presented and evolutionarily conserved source of major histocompatibility complex class I and II epitopes

### 2021-12-29 frontiers.tex
Refer to fig 4C, fix Q15

Also, for single- and multi-spanners, 
we determined the relevance of this finding by
calculating how much less SNPs are found in TMHs
when compared to soluble regions,
as depicted in figure \ref{fig:4}B.
In effect, per 1,000 SNPs found in soluble protein domains, 
one finds 978 SNPs in TMHs 
of single-spanners
and 911 SNPs in TMHs of multi-spanners.

>>>>

Also, for single- and multi-spanners, we determined the
relevance of this finding by calculating where and how much less SNPs
are found in TMHs when compared to soluble regions, as
depicted in Figure \ref{fig:4}B 
and \ref{fig:4}C.
In effect, per 1,000 SNPs found in soluble protein domains, 
one finds 978 SNPs in TMHs 
of single-spanners
and 911 SNPs in TMHs of multi-spanners.

### 2021-12-29 manuscript.tex
Fix title
Refer to fig 4C, fix Q15

% Affiliations
\usepackage{authblk}
\title{
  Transmembrane helices are 
  an overlooked and evolutionarily conserved
  source of major histocompatibility complex class I and II epitopes
}
\author[1]{Richèl J.C. Bilderbeek}
\author[1]{Maksim V. Baranov}
\author[1]{Geert van den Bogaart}
\author[1]{Frans Bianchi}
\affil[1]{GBB, University of Groningen, Groningen, The Netherlands}

@@

Also, for single- and multi-spanners, 
we determined the relevance of this finding by
calculating how much less SNPs are found in TMHs
when compared to soluble regions,
as depicted in figure \ref{fig:conservation_per_spanner}.
In effect, per 1,000 SNPs found in soluble protein domains, 
one finds 978 SNPs in TMHs 
of single-spanners
and 911 SNPs in TMHs of multi-spanners.

>>>>

% Affiliations
\usepackage{authblk}
\title{
  Transmembrane helices are an over-presented and evolutionarily conserved source of major histocompatibility complex class I and II epitopes
}
\author[1]{Richèl J.C. Bilderbeek}
\author[1]{Maksim V. Baranov}
\author[1]{Geert van den Bogaart}
\author[1]{Frans Bianchi}
\affil[1]{GBB, University of Groningen, Groningen, The Netherlands}

@@

Also, for single- and multi-spanners, we determined the
relevance of this finding by calculating where and how much less SNPs
are found in TMHs when compared to soluble regions, as
depicted in Figure \ref{fig:conservation_per_spanner} 
and \ref{fig:f_tmh_ncbi_per_spanner}
In effect, per 1,000 SNPs found in soluble protein domains, 
one finds 978 SNPs in TMHs 
of single-spanners
and 911 SNPs in TMHs of multi-spanners.
